Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Return value

\subsubsection{Relation}
Table \ref{} shows our data regarding how different relations influence maintainability. We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance. For these results, we have set the minimum amount of tokens for clones to 18 because otherwise the small clones dominate the results and turn them all towards unmaintainable.

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Row Labels & Maintainability Score & Number of Refactorings \\ \midrule
\rowcolor[HTML]{FFCCC9}
Common Hierarchy & 0,63 & 27 \\
Sibling & 0,53 & 664 \\
No Direct Superclass & 0,11 & 295 \\
Same Method & 0,06 & 740 \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,03 & 68 \\
Same Class & 0,02 & 1273 \\
External Superclass & 0,01 & 209 \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,06 & 36 \\
Same Interface & -0,07 & 269 \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,19 & 54 \\
External Ancestor & -0,28 & 154 \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,52 & 5 \\ \bottomrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

>>>>

\subsubsection{Relation}
Table \ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability. We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance. For these results, we have set the minimum amount of tokens for clones to 18 because otherwise the small clones dominate the results and turn them all towards unmaintainable.

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Category & Maintainability Score & Number of Refactorings \\ \midrule
\rowcolor[HTML]{FFCCC9}
Common Hierarchy & 0,63 & 27 \\
Sibling & 0,53 & 664 \\
No Direct Superclass & 0,11 & 295 \\
Same Method & 0,06 & 740 \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,03 & 68 \\
Same Class & 0,02 & 1273 \\
External Superclass & 0,01 & 209 \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,06 & 36 \\
Same Interface & -0,07 & 269 \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,19 & 54 \\
External Ancestor & -0,28 & 154 \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,52 & 5 \\ \bottomrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

\subsubsection{Return Value}
Table \ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Return Value & Maintainability Score & Number of Refactorings \\ \midrule
Return & 0,20 & 421 \\
Void & 0,19 & 2052 \\
Declare & 0,03 & 1318 \\
\rowcolor[HTML]{FFCCC9}
Assign & -1,29 & 3 \\ \bottomrule
\end{tabular}
\caption{Maintainability scores for different return values}
\label{tab:return}
\end{table}

\subsubsection{Arguments}
